---
title: "Assignment B1"
author: "Momenul Haque Mondol"
date: "(`r Sys.Date()`)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
#' @title  Calculating detailed summary of a numeric vector
#'
#' @description Provides five number summary (min, Q1, median, Q3, and max) of a numeric vector.
#' In addition, it calculates mean, IQR, range, and sd also.
#'
#' @param var numeric vector or a variable of data frame. 
#' Since the function applies on variable, I named the parameter as `var'.
#'
#'
#' @param na.rm a logical parameter. If na.rm = TRUE (default), 
#' it deletes the missing observation. It is common in other R functions as well.
#' 
#' @param ... further arguments passed to or from other methods.
#'
#' @return a tibble that contains all the basic summary.
#' 
#'  
#' @author Momenul Haque Mondol \email{mhmondol@student.ubc.ca}
#'
#'
#' @examples
#'
#' # loading package
#' suppressPackageStartupMessages(library(tidyverse))
#' 
#' # making summary of body_mass_g variable in palmerpenguins::penguins data set
#' palmerpenguins::penguins %>% 
#'  summarise(my_summary(body_mass_g, na.rm = TRUE))
#'  
#' # making summary of body_mass_g variable by grouping sex variable
#' 
#' palmerpenguins::penguins %>% 
#'  summarise(my_summary(body_mass_g, na.rm = TRUE))
#'
#'  
#'
#' 

# mail function starts here

 my_summary <- function(var, na.rm = TRUE, ...)
   {
     # Checking the var class.  
     if(!(class(var) %in% c("numeric", "integer")))
       {
          stop('I am so sorry, but this function only works for numeric input!\n',
               'You have provided an object of class: ', class(var)[1])
       }
     # Checking the missing values.   
     if(na.rm == FALSE && !missing(var))
       {
          stop(" There exist ", sum(is.na(var)) ," missing values in your variable!\n")
       }
     # Checking the vars length and giving warning!   
     if(length(var) < 2)
       {
          warning("Your vector has single element!
                   The standard deviation is not possible to calculate") 
       } 
   
      # Calculating summary starts here
      
      # Calculating central tendency measures.   
      min = min(var, na.rm = na.rm, ...)
      Q1 = stats::quantile(var, probs = .25, na.rm = na.rm, ...)
      mean = mean(var, na.rm = na.rm, ...)
      median = stats::median(var, na.rm = na.rm, ...)
      Q3 = stats::quantile(var, probs = .75, na.rm = na.rm, ...)
      max = max(var, na.rm = na.rm, ...)
      # Calculating dispersion measures.
      IQR = Q3 - Q1
      range = max - min
      sd = stats::sd(var, na.rm = na.rm)
      missing = sum(is.na(var))
      all_summary <- tibble_row(min=min, Q1=Q1, mean = mean,
                         median=median, Q3=Q3, max=max, IQR=IQR,
                         range=range, sd=sd, 'NAs' = missing)
      
      return(all_summary) 
      
   }
```      
      
      
 * An example is demonstrated for *penguins* data set in *palmerpenguins* R package. Summary statistics of **body_mass_g** can be found by running the following codes.     
  
```{r}
suppressPackageStartupMessages(library(tidyverse))


palmerpenguins::penguins %>% 
  summarise(my_summary(body_mass_g, na.rm = TRUE))

```




 * Summary statistics of **body_mass_g** variable for male and female separately.
 
```{r}


palmerpenguins::penguins %>% 
  group_by(sex) %>% 
  summarise(my_summary(body_mass_g, na.rm = TRUE))

```

Here, we found three rows although the sex has two categories. The third row is a summary of **body_mass_g** variable who didn't report the sex, e.g. NA.



 * If someone is interested to report a few summary instead, it allows to take a subset just mentioning the name of that specific measures.
 
```{r}
# reporting mean, and standard deviation only instead of detailed summary.

palmerpenguins::penguins %>% 
  group_by(sex) %>% 
  summarise(my_summary(body_mass_g, na.rm = TRUE)[c("mean", "sd")])

```



 * If someone is interested to report a few summary for 10% trimmed data set, it allows to calculate.
```{r}
# reporting 10% trimmed mean both from my_summary and mean function
palmerpenguins::penguins %>% 
  group_by(sex) %>% 
  summarise(From_my_summary = my_summary(body_mass_g, trim = .10, na.rm = TRUE)["mean"],
            From_mean=mean(body_mass_g, trim = .10, na.rm = TRUE))

```





 * The function will give warnings in case it gets a single value. But it can calculate all the summary measures but not the standard deviation. 
 
```{r}

palmerpenguins::penguins %>% 
  summarise(my_summary(body_mass_g[1], na.rm = TRUE))

```





 * Testing the **my_summary()** function by three conditions.
 
 
 
```{r}
suppressPackageStartupMessages(library(testthat))
test_that("Testing my_summary function", {
  expect_equal(my_summary(var = 1:10)[c("min", "max")], tibble(min=1, max=10))
  expect_error(my_summary(var = c("2", 3, 4)), "I am so sorry, but this function only works for numeric input!")
  expect_error(my_summary(var = c(NA, 3, 4), na.rm = FALSE), "missing values in your variable!")

  })


```



 


