---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mySummary

It is frequently required to find out basic summary statistics while analyzing data. One has to run multiple command to get a detailed summary of a numeric variable. That's why **mySummary** package can help getting a complete summary by a single function.


The goal of mySummary is to provide common  summary statistics for a numerical variable such as minimum, maximum, mean, median, inter-quartile range (IQR), standard deviation. In addition, it reports the missing values.

## Installation

You can install the development version of mySummary from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("momenulhaque/mySummary")
```

## Example

This is a basic example which shows you how to solve a common problem:


```{r}
# load the package first
library(mySummary)

# Defining a data set
Dat <- data.frame(age = c(40, 35, 27, 52, 29, 29, 46), sex = c("M", "F", "M", "F", "F", "M", "M"))

# Finding a detailed summary of age variable
mySummary(Dat$age)

# Finding a detailed summary of age variable for male only

mySummary(Dat[Dat$sex=="M", ]$age)
```


