---
title: "mySummary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mySummary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Introduction

It is frequently required to find out basic summary statistics while analyzing data. The common  summary statistics for a numerical variable are minimum, maximum, mean, median, inter-quartile range (IQR), standard deviation. The *mySummary* package is intended to provide all the basic summary statistics of a numeric variable. In addition, it reports the missing values.

# Installation
Since the package isn't uploaded to CRAN, it requires to install from Github repository. The following code would drive one to install the package and load it.

```{r}
devtools::install_github("momenulhaque/mySummary")
library(mySummary)

```

# Usage

```{r}
# Defining a data set
Dat <- data.frame(age = c(40, 35, 27, 52, 29, 29, 46), sex = c("M", "F", "M", "F", "F", "M", "M"))

# Finding a detailed summary of age variable
mySummary(Dat$age)

# Finding a detailed summary of age variable for male only

mySummary(Dat[Dat$sex=="M", ]$age)
```


